---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# apecsutils

<!-- badges: start -->
<!-- badges: end -->

The goal of `apecsutils` is to make some simple data management tasks for APECS simpler.

Currently it helps with:

- checking access permissions on data packages
- adding access permissions to data packages

## Installation

You can install the development version of `apecsutils` from GitHub using:

```{r eval=FALSE}
remotes::install_github("NCEAS/arcticdatautils")
remotes::install_github("mbjones/apecsutils")
```

## Example

This is a basic example which shows you how to solve the common problem when a
member of the APECS lab does not have sufficient permissions to manage a data package.

Note, for any of these to work, you need to be logged in to the KNB repository,
and set your access token in the R `options` so R can identify you. You can get 
this token from your KNB profile settings. Paste the token for into the console, and not
into a script, as you don't want to save this, and you should treat it like a secret password.

```{r set_token, eval=FALSE}
options(dataone_token = "eyJhbGciOiJSUzI1NiJ9.eyJzdW...continuing_as_a_very_long_random_string")
```

Once we are logged in, we can check that both the lab leader and the SME Group has `changePermission` permission
on the package, and then we update the package to add these permissions.

```{r check_access, eval=FALSE}
library(apecsutils)

# Identify a package by its identifier (pid) from the KNB repository
pid <- "resource_map_urn:uuid:22896aa3-38fd-4baa-888f-cea4b908309c"

# These are the identifiers for the lab leader and the lab group
ginny <- "http://orcid.org/0000-0002-7538-7081"
sme_group <- "CN=Sustainable Marine Ecosystems in Alaska Lab,DC=dataone,DC=org"

# Check if both ginny and sme_group have all permissions
check_package_access(pid, subjects = c(ginny, sme_group), permissions = c("read", "write", "changePermission"))
```
Finally, you can update the package to allow full access (or whatever access needed) by Ginny and the Group, and show that the results have changed by checking the status again.

```{r set_access, eval=FALSE}
# Add permissions for both ginny and sme_group at all levels of access (YMMV)
add_package_access(pid, subjects = c(ginny, sme_group), permissions = c("read", "write", "changePermission"))

# Check if both ginny and sme_group have all permissions now
check_package_access(pid, subjects = c(ginny, sme_group), permissions = c("read", "write", "changePermission"))
```

